Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/Virgo Network

### 2013-07-30 doc/paper.tex
added vicky's and diego's comments, and finalized the draft

Within the next five years, the Advanced LIGO/Virgo network will have
reached a sensitivity sufficient to enable the routine detection of
gravitational waves.  Beyond the initial detection, the scientific
promise of these instruments relies on the effectiveness of our
parameter estimation techniques. The majority of this effort has been towards the
detection and characterization of gravitational waves from compact
binary coalescence, e.g. the coalescence of binary neutron stars.
While several previous studies have focused on the parameter
estimation abilities of advanced detectors, the majority have relied
on approximation techniques such as the Fisher Matrix.  We report the
statistical uncertainties that will be achievable, in practice, using
the full parameter estimation machinery developed by the LIGO/Virgo
Collaboration.  We find the recovery of the individual masses to be
fractionally within 10\% at the 65\% credible intervals for equal-mass
systems, and within 2\% for unequal-mass systems.  We also report the
average uncertainties on the sky-locations, luminosity distances, and
orbital inclinations of ideal detection candidates that can be
achieved by different network configurations.
% \will{I'm not sure that
  %we want to say this exactly this way---the sources in this study are
 % not randomly distributed in SNR, but rather cluster at rather loud
  %signals.}
\end{abstract}

@@

Within the next few years, the first generation of gravitational-wave
detectors capable of regularly resolving astrophysical sources will
come online \citep{AdvLIGO,AdvVirgo}.  The Advanced LIGO and Advanced Virgo
detectors will provide the first insights into the final moments of
binary compact object mergers, including the mergers of binary neutron
star systems.  Intense preparations are underway to characterize and
extract as much physical information as possible from these signals.

The mergers of binary neutron stars (BNS) are expected to be one of the most
common compact binary sources in the advanced detector era.  %\will{This
  %is technically true (thanks to the word ``expected''), but the
 % uncertainty in rates is so large that it would not be surprising at
 % all for it to be wrong.  Re-word or eliminate.} Added "one of the "
  Models from stellar
evolution and observations of binary pulsars suggest that the number
of BNS mergers within Advanced LIGO/Virgo's detection
horizon could reach several tens to hundreds each year
\citep{RatesPaper}.  Although the peak sensitivity of ground-based
detectors is not focused on the frequency at which BNS systems merge,
it could still be possible to extract information about both strong
field gravitational physics \citep{Li2012} and the the equation of state of
dense nuclear matter
\citep{HindererBNS2010}.  Furthermore, the observations of multiple BNS systems
will provide key insights into the evolution of binary systems in the
field \citep{VickyRates,KimRates} . As such, BNS systems will likely
form the ``bread and butter'' of the compact binary coalescence
detection effort in the coming years.

@@

By employing the full parameter-estimation machinery that will
eventually be used in the Advanced LIGO/Virgo era, our results give
 estimates at the realistic capabilities of
advanced ground-based detectors to characterize BNS systems.  Until
recently, the majority of studies have employed the Fisher-matrix
formalism which was first adapted for gravitational-wave parameter
estimation by \citet{FinnDetection}.  While each of these studies
\citep{PoissonWill,CutlerFlanagan,ArunPE} have pointed out the
limitations and flaws of the Fisher Information Matrix, there has been
no study which investigates the BNS parameter estimation capabilities
of Advanced LIGO/Virgo using the techniques that will eventually be
employed.  The recent work of \cite{Vallisneri} and our own work
\citep{Inadequacies} has demonstrated that the Fisher matrix cannot
even be treated as a lower bound on the standard deviations of certain
parameters (particularly the masses) measurable in gravitational-wave
detectors.

In this paper, we perform a systematic study of the statistical
uncertainties with which the Advanced LIGO/Virgo network will be able
to measure the basic parameters of BNS mergers.  In Section
\ref{PEsection}, we describe the machinery of our parameter estimation
code, \texttt{LALInference}, and the associated MCMC sampler,
\texttt{lalinference\_mcmc}, as well as the frequency-domain
gravitational-wave template we employ.  In Section
\ref{resultsSection}, we qualitatively analyze the posterior
probability density functions for BNS systems with different masses
and extrinsic parameters.  We select three equal-mass and one unequal-mass
 binary systems as fiducial examples of BNS systems.  Each system was then analyzed 40 
 times with isotropically selected sky locations and orbital orientations, and with a distance
 such that each signal was injected with a signal-to-noise ratio of 20.
  The results are divided into three subsections of interest: the recovery of the mass
parameters (Section \ref{massSection}), the recovery of the orbital
inclination and luminosity distance (Section \ref{idSection}), and the
localization of sources on the sky (Section \ref{skySection}).
Finally we provide quantitative 1-dimensional credible intervals on
each parameter in Section \ref{ciSection}.  These results, contained
in Tables \ref{ciTableIntrinsic} and \ref{ciTableExtrinsic}, are
intended as a reference for the optimal BNS parameter estimation
capabilities of Advanced LIGO/Virgo.  We assume that $G=c=1$
throughout.

@@

We begin by introducing a Bayesian formalism for parameter estimation.
%Before offering a brief derivation of the FIM, a few preliminary
%techniques must be introduced.  First,
We assume that the time-domain signal in a gravitational-wave network
can be written as the sum of a gravitational waveform $h_0$ and
the noise of the detector $n$.  We further assume that this noise is
stationary and Gaussian with zero mean.  The detector output is simply
\begin{equation}
s = n + h_0 .
\label{SignalAddition}
\end{equation}
Since the noise model is Gaussian, we can write the probability of a
specific signal realization $s$ given an input waveform $h(\thpara)$ as
proportional to the probability that the residual is Gaussian
distributed once the waveform has been subtracted
\begin{align}
  p(s | \thpara) &\propto \exp\left[-\frac{1}{2}\left<n|n
    \right>\right] \nonumber \\ &= \exp\left[-\frac{1}{2}\left < s -
    h(\thpara) | s-h(\thpara)\right >\right] ,
  \label{likelihood}
\end{align}
where $\thpara$ is the set of parameters for the template waveforms.
The quantity $p(s | \thpara)$ is the likelihood of the signal $s$
given the parameters $\thpara$.  The inner product, $\left< ~|~
\right> $, is defined using the noise spectrum of the detectors as
\begin{equation}
  \left<a|b\right> \equiv 4 \Re \int
  \frac{\tilde{a}(f)\tilde{b}^*(f)}{S_n(f)} df ,
  \label{innerProduct}
\end{equation}
where $S_n(f)$ is the one-sided power-spectral density (PSD) as a
function of frequency, and $\tilde{a}(f)$ and $\tilde{b}(f)$ are the
Fourier transforms of the time-domain data $a(t)$ and $b(t)$.  If we
pick a set of parameters $\thpara$ such that $h(\thpara) = h_0$, then
the posterior \eqref{posterior} will be near a global maximum;
however, the presence of noise will in general deflect the maximum of
our posterior away from the value at $h(\thpara) = h_0$.  Therefore, the
maximum posterior parameters do not necessarily correspond to the true
parameters of the source; when interpreting parameter estimation
results it is important to consider the full posterior distribution
function.

@@

@@

When dealing with a network of gravitational-wave detectors, the SNRs
of the individual detectors add in quadrature.  That is, the network
SNR for a detection is

@@

For this study, we consider four separate populations of BNS systems,
with component mass combinations of $1M_{\odot}/1M_{\odot}$,
$1.4M_{\odot}/1.4M_{\odot}$, $1M_{\odot}/2.5M_{\odot}$, and
$2.5M_{\odot}/2.5M_{\odot}$.  Each population consisted of 40 signals
distributed randomly in sky location, polarization, inclination,
time-of-arrival, and coalescence phase.  The luminosity distance, $D$,
was selected to provide a network SNR of $\rho_{\text{network}}=20$
for each source.  While unphysical from an astrophysics perspective
(binary sources should be distributed evenly in comoving volume), this
choice allows us to explore the parameter estimation in the context of
loud but plausible detection candidates.

@@

We find that there is virtually no difference between the mass PDFs of
our different injected signals within each mass bin.  While this may
initially seem disconcerting, it is to be expected.  Recall that all
of the BNS signals were injected with a network SNR of 20 into a
zero-noise detector realization.  Furthermore, note that the mass
parameters are the only two which directly affect the phase of the
TaylorF2 waveform \eqref{phase}.  Therefore, as long as the injected
mass parameters are identical within each mass system, and as long as
the injected SNR is identical, the amount of recoverable information
in each mass parameter should be almost identical, and for a
sufficiently converged MCMC chain, the recovered posterior PDF should
be identical.

@@

Unfortunately, this will not be feasible in practice.  We have
neglected the spin of the binaries, which will be highly correlated to
the masses.  This coupling means that a higher-massed spinning black
hole systems can produce waveforms very similar to non-spinning,
low-mass systems, making it extremely difficult to discern between
non-spinning neutron stars and spinning, more massive black holes
\citep{Baird2013,Hannam2013}.  However, the situation is not hopeless:
if the spins are misaligned, the spin vectors will couple to the
orientation of the binary (encoded in the three angles $\phi_0$,
$\iota$, and $\psi$) via relativistic precession.  It remains to be
seen if using fully spinning waveforms will make it possible for
Advanced\ LIGO/Virgo to discern binary neutron stars from their
spinning black hole counterparts.

@@

The sky location uncertainties for HLV and HLVI are shown in Figures
\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI} respectively.  We show
all four mass bins together, since in practice the mass of the signals
has little effect on the recovery of the sky location for the
considered BNS systems.  Only the location on the sky, the network
configuration, and the other extrinsic parameters were found to be
relevant.  In particular, notice the increase in efficiency between
the HLV configuration and the HLVI configuration.  In the HLV
configuration, there exist points on the sky in which the signal was
injected near the plane of the detector network.  This causes the
elongated, ``banana-shaped'' PDFs seen in Figure \ref{2525SkyLocHLV}.
In the HLVI configuration, the plane is no longer relevant, and there
are substantially fewer regions in which only two detectors see a
sufficiently strong signal.  See \cite{Veitch2012} for a more detailed
comparison of the sky-localization benefits of the HLVI configuration
versus the three-detector network.  The quantitative
results for the two network configurations are again reported in Table
\ref{ciTableExtrinsic}.

@@

We have performed the current analysis on zero-noise injections for
two reasons.  First, the results of a zero-noise analysis are
similar to those that would be achieved by averaging the results of
multiple identical injections in different Gaussian noise
realizations, as was argued in Section \ref{waveformSection}.  The second reason 
is we are not able
to predict the characteristics of realistic (often non-Gaussian)
advanced detector noise.  Attempting to do so would have little chance
of being accurate while requiring a huge computational burden to
combine the results of many MCMC runs in different noise realizations.

@@

When quoting parameter estimation results, it is often convenient to
reduce the full parameter space to credible intervals about single
marginalized parameters..  To that end, we state the averaged 65\%
intervals about the single parameters for each of the three
parameter pairs of interest.  These were already plotted for the sky
locations in Figures~\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI}.

@@

In Table~\ref{ciTableIntrinsic}, we list the mean 65\% confidence
intervals recovered for the four mass configurations in both network
configurations. This essentially quantifies the widths of the
posteriors plotted throughout Section~\ref{resultsSection}.  The
purpose of Tables~\ref{ciTableIntrinsic} and \ref{ciTableExtrinsic} is
to provide a quantitative and quotable source for studies seeking to
determine how well a physical question about BNS systems can be
answered with the Advanced LIGO/Virgo network.

\begin{table*}[t!]
\centering
\caption{Mean 65\% confidence intervals for intrinsic parameters for
  each of the four systems considered.  We report the confidence
  intervals of quantities measured, as well as the component masses
  and total mass.  Although the results for the HLV and HLVI
  configurations are quantitatively identical, we report them
  separately for consistency.}
\begin{tabular}{lcccccccccc}

\\HLVI\\ \hline\hline System & \vline & $\Delta \chmass / \chmass$ &
\vline & $\Delta M_1 / M_1$ & \vline & $\Delta M_2 / M_2$ & \vline &
$\Delta M_{tot}/M_{tot}$ & \vline & $\Delta q$\\ \hline\hline
$1M_{\odot}-1M_{\odot}$ & \vline & $4.70\times 10^{-5}$ & \vline &
$6.83\times 10^{-2}$ & \vline & $6.09\times 10^{-2}$ & \vline &
$3.67\times 10^{-3}$ & \vline & $1.17\times 10^{-1}$\\ \hline
$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $8.27\times 10^{-5}$ & \vline &
$7.27\times 10^{-2}$ & \vline & $6.45\times 10^{-2}$ & \vline &
$4.10\times 10^{-3}$ & \vline & $1.24\times 10^{-1}$ \\ \hline
$1M_{\odot}-2.5M_{\odot}$ & \vline & $1.65\times 10^{-4}$ & \vline &
$1.74\times 10^{-2}$ & \vline & $1.49\times 10^{-2}$ & \vline &
$8.15\times 10^{-3}$ & \vline & $1.29\times 10^{-2}$\\\hline
$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $2.29\times 10^{-4}$ & \vline &
$8.52\times 10^{-2}$ & \vline & $7.41\times 10^{-2}$ & \vline &
$5.51\times 10^{-3}$ & \vline & $1.41\times 10^{-1}$\\ \hline\hline

@@

\hline\hline System & \vline & $\Delta \chmass / \chmass$ & \vline &
$\Delta M_1 / M_1$ & \vline & $\Delta M_2 / M_2$ & \vline & $\Delta
M_{tot}/M_{tot}$ & \vline & $\Delta q$\\ \hline\hline
$1M_{\odot}-1M_{\odot}$ & \vline & $4.66\times 10^{-5}$ & \vline &
$6.82\times 10^{-2}$ & \vline & $6.09\times 10^{-2}$ & \vline &
$3.64\times 10^{-3}$ & \vline & $1.17\times 10^{-1}$ \\ \hline
$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $8.31\times 10^{-5}$ & \vline &
$7.35\times 10^{-2}$ & \vline & $6.51\times 10^{-2}$ & \vline &
$4.18\times 10^{-3}$ & \vline & $1.25\times 10^{-1}$\\ \hline
$1M_{\odot}-2.5M_{\odot}$ & \vline & $1.65\times 10^{-4}$ & \vline &
$1.75\times 10^{-2}$ & \vline & $1.50\times 10^{-2}$ & \vline &
$8.19\times 10^{-3}$ & \vline & $1.30\times 10^{-2}$ \\ \hline
$2.5M_{\odot}-2.5M_{\odot}$ & \vline & $2.30\times 10^{-4}$ & \vline &
$8.53\times 10^{-2}$ & \vline & $7.42\times 10^{-2}$ & \vline &
$5.52\times 10^{-3}$ & \vline & $1.41\times 10^{-1}$ \\ \hline\hline

\end{tabular}
\label{ciTableIntrinsic}
\end{table*}

\begin{table*}[t!]
\centering
\caption{Mean 65\% confidence intervals of extrinsic parameters for
  each of the four systems considered.  As expected, there exists a
  substantial improvement in the sky localization capabilities of the
  four-detector HLVI configuration over the three-detector HLV
  configuration.  Note that the solid-angle sky-location confidence
  intervals, $\Delta\Omega$, are calculated directly on the 2D sphere,
  not by combining the $\alpha$ and $\delta$ uncertainties.}
\begin{tabular}{lcccccccccc}

\\HLVI\\ \hline\hline System & \vline & $\Delta D$ $(mpc)$ & \vline &
$\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline &
$\Delta \delta$ $(deg)$ & \vline & $\Delta\Omega$
$(deg^2)$\\ \hline\hline $1M_{\odot}-1M_{\odot}$ & \vline &
$3.64\times 10^{1}$ & \vline & $2.23\times 10^{-1}$ & \vline & $1.45$
& \vline & $1.48$ & \vline & $1.88$\\ \hline
$1.4M_{\odot}-1.4M_{\odot}$ & \vline & $5.52\times 10^{1}$ & \vline &
$2.56\times 10^{-1}$ & \vline & $1.49$ & \vline & $1.50$ & \vline &
$2.26$\\ \hline $1M_{\odot}-2.5M_{\odot}$ & \vline & $6.48\times
10^{1}$ & \vline & $2.93\times 10^{-1}$ & \vline & $1.54$ & \vline &
$1.64$ & \vline & $2.10$\\ \hline $2.5M_{\odot}-2.5M_{\odot}$ & \vline
& $1.06\times 10^{2}$ & \vline & $2.99\times 10^{-1}$ & \vline &
$1.03\times 10^{1}$ & \vline & $1.61$ & \vline & $2.22$\\ \hline\hline

>>>>

Within the next five years, it is expected that the Advanced LIGO/Virgo network will have
reached a sensitivity sufficient to enable the routine detection of
gravitational waves.  Beyond the initial detection, the scientific
promise of these instruments relies on the effectiveness of our physical
parameter estimation capabilities. The majority of this effort has been towards the
detection and characterization of gravitational waves from compact
binary coalescence, e.g. the coalescence of binary neutron stars.
While several previous studies have investigated the accuracy of parameter
estimation with advanced detectors, the majority have relied
on approximation techniques such as the Fisher Matrix.  Here we report the
statistical uncertainties that will be achievable using
the full parameter estimation machinery developed by the LIGO/Virgo
Collaboration via Markov-Chain Monte Carlo methods. 
 We find the recovery of the individual masses to be
fractionally within 8.5\% (13.4\%) at the 65\% (90\%) credible intervals for equal-mass
systems, and within 2\% (3.1\%) for unequal-mass systems.  We also find that the Advanced
LIGO/Virgo network will constrain the locations of binary neutron star mergers to an average
 uncertainty of $7.4$ $\mathrm{deg}^2$ (18.6 $\mathrm{deg}^2$) on the sky.  This region is improved to  2.2 $\mathrm{deg}^2$ $(5$ $\mathrm{deg}^2)$ with the addition of the proposed LIGO India detector to the network.  We also report the
average uncertainties on the luminosity distances and
orbital inclinations of ideal detection candidates that can be
achieved by different network configurations.
% \will{I'm not sure that
  %we want to say this exactly this way---the sources in this study are
 % not randomly distributed in SNR, but rather cluster at rather loud
  %signals.}
\end{abstract}

@@

Within the next few years, the first generation of gravitational-wave
interferometers capable of regularly detecting astrophysical sources will
come online \citep{AdvLIGO,AdvVirgo}.  The Advanced LIGO and Advanced Virgo
detectors (and the anticipated LIGO India detector)
 will provide the first insights into the final moments of
binary compact object mergers, including the mergers of binary neutron
star systems.  Intense preparations are underway to characterize and
extract as much physical information as possible from these signals.

The mergers of binary neutron stars (BNS) are expected to be one of the most
common compact binary sources in the advanced detector era.  %\will{This
  %is technically true (thanks to the word ``expected''), but the
 % uncertainty in rates is so large that it would not be surprising at
 % all for it to be wrong.  Re-word or eliminate.} Added "one of the "
  Models from stellar
evolution and observations of binary pulsars suggest that the number
of BNS mergers within Advanced LIGO/Virgo's detection
horizon could reach several tens to hundreds each year
\citep{RatesPaper}.  Although the peak sensitivity of ground-based
detectors is not focused on the frequency at which BNS systems merge,
it could still be possible to extract information about both strong
field gravitational physics \citep{Li2012} and the the equation of state of
dense nuclear matter
\citep{HindererBNS2010}.  Furthermore, the observations of multiple BNS systems
will provide key insights into the evolution of binary systems in the
field \citep{VickyRates,KimRates,OsowskiRates2011,RichardRates2010} . As such, BNS systems will likely
form the ``bread and butter'' of the compact binary coalescence
detection effort in the coming years.

@@

By employing the full parameter-estimation machinery that will
eventually be used in the Advanced LIGO/Virgo era, our results
 give estimates of the realistic capabilities of
advanced ground-based detectors to characterize BNS systems.  Until
recently, the majority of studies have employed the Fisher-matrix
formalism which was first adapted for gravitational-wave parameter
estimation by \citet{FinnDetection}.  While each of these studies
\citep{PoissonWill,CutlerFlanagan,ArunPE} have pointed out the
limitations and flaws of the Fisher Information Matrix, there has been
no study which investigates the BNS parameter estimation capabilities
of Advanced LIGO/Virgo using the techniques that will eventually be
employed.  The recent work of \cite{Vallisneri} and our own work
\citep{Inadequacies} has demonstrated that the Fisher matrix cannot
even be treated as a lower bound on the standard deviations of certain
parameters (particularly the masses) measurable in gravitational-wave
detectors.

In this paper, we perform a systematic study of the statistical
uncertainties with which the Advanced LIGO/Virgo network will be able
to measure the basic parameters of BNS mergers.  In Section
\ref{PEsection}, we describe the machinery of our parameter estimation
code, \texttt{LALInference}, and the associated MCMC sampler,
\texttt{lalinference\_mcmc}, as well as the frequency-domain
gravitational-wave template we employ.  In Section
\ref{resultsSection}, we qualitatively analyze the posterior
probability density functions for BNS systems with different masses
and extrinsic parameters.  We select three equal-mass and one unequal-mass
 binary systems as prototypical examples of BNS systems.  Each system is analyzed 40 
 times with isotropically selected sky locations and orbital orientations, and with a distance
 such that each signal was injected with a network signal-to-noise ratio of 20.
  The results are divided into three subsections of interest: the recovery of the mass
parameters (Section \ref{massSection}), the recovery of the orbital
inclination and luminosity distance (Section \ref{idSection}), and the
localization of sources on the sky (Section \ref{skySection}).
Finally we provide quantitative 1-dimensional credible intervals on
each parameter in Section \ref{ciSection}.  These results, contained
in Tables \ref{ciTableIntrinsic} and \ref{ciTableExtrinsic}, are
intended as a reference for the optimal BNS parameter estimation
capabilities of Advanced LIGO/Virgo.  We assume that $G=c=1$
throughout.

@@

We begin by introducing a Bayesian formalism for parameter estimation.
%Before offering a brief derivation of the FIM, a few preliminary
%techniques must be introduced.  First,
We assume that the time-domain signal in a gravitational-wave network
can be written as the sum of a gravitational waveform $h_0$ and
the noise of the detector $n$.  We further assume that this noise is
stationary and Gaussian with zero mean.  The detector output is simply
\begin{equation}
s = n + h_0 .
\label{SignalAddition}
\end{equation}
Since the noise model is Gaussian, we can write the probability of a
specific signal realization $s$ given an input waveform $h(\thpara)$ as
proportional to the probability that the residual is Gaussian
distributed once the waveform has been subtracted
\begin{align}
  p(s | \thpara) &\propto \exp\left[-\frac{1}{2}\left<n|n
    \right>\right] \nonumber \\ &= \exp\left[-\frac{1}{2}\left < s -
    h(\thpara) | s-h(\thpara)\right >\right] ,
  \label{likelihood}
\end{align}
where $\thpara$ is the set of parameters for the template waveforms.
The quantity $p(s | \thpara)$ is the likelihood of the signal $s$
given the parameters $\thpara$.  The inner product, $\left< ~|~
\right> $, is defined using the noise spectrum of the detectors as
\begin{equation}
  \left<a|b\right> \equiv 4 \Re \int
  \frac{\tilde{a}(f)\tilde{b}^*(f)}{S_n(f)} df ,
  \label{innerProduct}
\end{equation}
where $S_n(f)$ is the one-sided power-spectral density (PSD) as a
function of frequency, and $\tilde{a}(f)$ and $\tilde{b}(f)$ are the
Fourier transforms of the time-domain data $a(t)$ and $b(t)$.  If we
pick a set of parameters $\thpara$ such that $h(\thpara) = h_0$, then
the likelihood \eqref{likelihood} will be near a global maximum;
however, the presence of noise will in general deflect the maximum of
our likelood away from the value at $h(\thpara) = h_0$.  Therefore, the
maximum likelihood parameters do not necessarily correspond to the true
parameters of the source.

@@

  \subsection{Detector Configuration and Noise Models}
  \label{detectorSection}

@@

\noindent When dealing with a network of gravitational-wave detectors, the SNRs
of the individual detectors add in quadrature.  That is, the network
SNR for a detection is

@@

For this study, we consider four separate populations of BNS systems,
with component mass combinations of $1M_{\odot}/1M_{\odot}$,
$1.4M_{\odot}/1.4M_{\odot}$, $1M_{\odot}/2.5M_{\odot}$, and
$2.5M_{\odot}/2.5M_{\odot}$.  Each population consisted of 40 signals
distributed randomly in sky location, polarization, inclination,
time-of-arrival, and coalescence phase.  The luminosity distance, $D$,
was selected to provide a network SNR of $\rho_{\text{network}}=20$
for each source.  While unphysical from an astrophysics perspective
(binary sources are expected to be distributed uniformly in comoving volume), this
choice allows us to explore the parameter estimation in the context of
loud but plausible detection candidates.

@@

We find that there is virtually no difference between the mass PDFs of
our different injected signals within each mass bin.  While this may
initially seem disconcerting, it is to be expected for the analysis presented here.
  Recall that all
of the BNS signals were injected with a network SNR of 20 into a
zero-noise detector realization.  Furthermore, note that the mass
parameters are the only two which directly affect the phase of the
TaylorF2 waveform \eqref{phase}.  Therefore, as long as the injected
mass parameters are identical within each mass system, and as long as
the injected SNR is identical, the amount of recoverable information
in each mass parameter should be almost identical, and for a
sufficiently converged MCMC chain, the recovered posterior PDF should
be identical.

@@

In practice, there is a physical complication to this claim: we have
neglected the spin of the binaries, which will be highly correlated to
the masses.  This coupling means that, in the case where the black hole spins
are parallel to the orbital angular momentum, a higher-massed spinning black
hole systems can produce waveforms very similar to non-spinning,
low-mass systems.  This effect makes it extremely difficult to discern between
non-spinning neutron stars and spin-aligned, more massive black holes
\citep{Baird2013,Hannam2013}.  However, the situation is not hopeless:
if the spins are misaligned, the spin vectors will couple to the
orientation of the binary (encoded in the three angles $\phi_0$,
$\iota$, and $\psi$) via relativistic precession.  It remains to be
seen if using fully spinning waveforms will make it possible for
Advanced\ LIGO/Virgo to discern binary neutron stars from their
spinning black hole counterparts.

@@

The sky location uncertainties for HLV and HLVI are shown in Figures
\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI} respectively.  We show
all four mass bins together, since in practice the mass of the signals
has little effect on the recovery of the sky location for the
considered BNS systems.  Only the location on the sky, the network
configuration, and the other extrinsic parameters were found to be
relevant.  In particular, notice the increase in efficiency between
the HLV configuration and the HLVI configuration.  In the HLV
configuration, there exist points on the sky in which the signal was
injected near the plane of the detector network.  This causes the
elongated, ``banana-shaped'' PDFs seen in Figure \ref{2525SkyLocHLV}.
In the HLVI configuration, the plane is no longer relevant, and there
are substantially fewer regions in which only two detectors see a
sufficiently strong signal.  See \cite{Veitch2012} for a more detailed
comparison of the sky-localization benefits of the HLVI configuration
versus the three-detector network.  For the HLV configuration, we find that
 all of the signals are recovered with
a solid angle uncertainty of less than 60 $\mathrm{deg}^2$ (120 $\mathrm{deg}^2$)
at the 65\% (90\%) credible interval, while the HLVI configuration 
recovers all signals to less than 13 $\mathrm{deg}^2$ (34 $\mathrm{deg}^2$).
The mean quantitative results for the two network configurations show a similar
 benefit with the addition of LIGO India, and are again reported in
  Table \ref{ciTableExtrinsic}.

@@

We have performed the current analysis on zero-noise injections for
two reasons.  First, the results of a zero-noise analysis are
similar to those that would be achieved by averaging the results of
multiple identical injections in different Gaussian noise
realizations, as was argued in Section \ref{detectorSection}.  The second reason 
is we are not able
to predict the characteristics of realistic (often non-Gaussian)
advanced detector noise.  Attempting to do so would have little chance
of being accurate while requiring a huge computational burden to
combine the results of many MCMC runs in many different noise realizations.

@@

When quoting parameter estimation results, it is often convenient to
reduce the full parameter space to credible intervals about single
marginalized parameters..  To that end, we state the averaged 65\% and 90\% credible
intervals about the single parameters for each of the three
parameter pairs of interest.  These were already plotted for the sky
locations in Figures~\ref{2525SkyLocHLV} and \ref{2525SkyLocHLVI}.

@@

In Table~\ref{ciTableIntrinsic}, we list the mean 65\% and 90\% credible
intervals recovered for the four mass configurations in both network
configurations. This essentially quantifies the widths of the
posteriors plotted throughout Section~\ref{resultsSection}.  The
purpose of Tables~\ref{ciTableIntrinsic} and \ref{ciTableExtrinsic} is
to provide a quantitative and quotable source for studies seeking to
determine how well a physical question about BNS systems can be
answered with the Advanced LIGO/Virgo network.

Given the previous reliance of parameter estimation studies on the Fisher
Information Matrix, it is informative to compare the credible intervals quoted here 
to previously reported values in the literature.  We recompute the credible intervals 
of the chirp mass and the symmetric mass ratio ($\eta \equiv m_1 m_2 / M_{tot}^2$)
at the 68\% level (1-$\sigma$) for the $1.4M_{\odot}/1.4M_{\odot}$ system presented 
here.  We then compare the findings of the MCMC to the Fisher matrix predictions using
an identical network configuration (HLV), noise curve, and waveform model.  
We compute the Fisher matrix uncertainties 
using a code previously described in \cite{Inadequacies}.  We find that the MCMC credible
 intervals vary significantly from
the estimates of the Fisher matrix, with the Fisher matrix underestimating the 
fractional uncertainties by as much as a factor of three.  See Table~\ref{FIMvsMCMC}.
   This disagreement, while 
   unsurprising, emphasizes the importance of employing the full parameter estimation
    machinery of an MCMC when making physically relevant claims.

\begin{table*}[t!]
\centering
\caption{Mean 65\% and 90\% credible intervals for intrinsic parameters for
  each of the four systems considered.  We report the credible
  intervals of quantities measured, as well as the component masses
  and total mass.  Although the results for the HLV and HLVI
  configurations are quantitatively identical, we report them
  separately for consistency.}
  \tabcolsep=0.11cm
      {\renewcommand{\arraystretch}{1.3} 
\begin{tabular}{lcccccccccccccccccccc}

\\HLVI\\

 \hline\hline System & \vline & \multicolumn{3}{c}{$\Delta \chmass / \chmass$} &
\vline & \multicolumn{3}{c}{$\Delta M_1 / M_1$} & \vline & \multicolumn{3}{c}{$\Delta M_2 / M_2$} & \vline &
\multicolumn{3}{c}{$\Delta M_{tot}/M_{tot}$} & \vline & \multicolumn{3}{c}{$\Delta q$}\\ \hline
Credible Level & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% \\
\hline\hline

$1M_{\odot}-1M_{\odot}$ & \vline &$0.00465\%$ & \vline &$0.00863\%$ & \vline & $6.78\%$ & \vline &$10.6\%$ & \vline & $6.06\%$ & \vline &$9.28\%$ & \vline & $0.362\%$ & \vline &$0.633\%$ & \vline & $0.117$ & \vline &$0.178$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00827\%$ & \vline &$0.0154\%$ & \vline & $7.27\%$ & \vline &$11.4\%$ & \vline & $6.45\%$ & \vline &$9.90\%$ & \vline & $0.410\%$ & \vline &$0.724\%$ & \vline & $0.124$ & \vline &$0.189$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0165\%$ & \vline &$0.0294\%$ & \vline & $1.74\%$ & \vline &$3.10\%$ & \vline & $1.49\%$ & \vline &$2.67\%$ & \vline & $0.815\%$ & \vline &$1.46\%$ & \vline & $0.0129$ & \vline &$0.0231$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.0229\%$ & \vline &$0.0424\%$ & \vline & $8.52\%$ & \vline &$13.3\%$ & \vline & $7.42\%$ & \vline &$11.4\%$ & \vline & $0.551\%$ & \vline &$0.958\%$ & \vline & $0.141$ & \vline &$0.215$\\

\hline
\hline

@@

 \hline\hline System & \vline & \multicolumn{3}{c}{$\Delta \chmass / \chmass$} &
\vline & \multicolumn{3}{c}{$\Delta M_1 / M_1$} & \vline & \multicolumn{3}{c}{$\Delta M_2 / M_2$} & \vline &
\multicolumn{3}{c}{$\Delta M_{tot}/M_{tot}$} & \vline & \multicolumn{3}{c}{$\Delta q$}\\ \hline
Credible Level & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% & \vline & 65\% & \vline & 90\% \\
\hline\hline

$1M_{\odot}-1M_{\odot}$ & \vline &$0.00466\%$ & \vline &$0.00865\%$ & \vline & $6.82\%$ & \vline &$10.5\%$ & \vline & $6.09\%$ & \vline &$9.25\%$ & \vline & $0.364\%$ & \vline &$0.633\%$ & \vline & $0.117$ & \vline &$0.177$\\\hline$1.4M_{\odot}-1.4M_{\odot}$ & \vline &$0.00831\%$ & \vline &$0.0155\%$ & \vline & $7.35\%$ & \vline &$11.5\%$ & \vline & $6.51\%$ & \vline &$10.0\%$ & \vline & $0.418\%$ & \vline &$0.743\%$ & \vline & $0.125$ & \vline &$0.191$\\\hline$1M_{\odot}-2.5M_{\odot}$ & \vline &$0.0165\%$ & \vline &$0.0295\%$ & \vline & $1.75\%$ & \vline &$3.11\%$ & \vline & $1.50\%$ & \vline &$2.67\%$ & \vline & $0.819\%$ & \vline &$1.46\%$ & \vline & $0.0130$ & \vline &$0.0232$\\\hline$2.5M_{\odot}-2.5M_{\odot}$ & \vline &$0.023\%$ & \vline &$0.0428\%$ & \vline & $8.53\%$ & \vline &$13.4\%$ & \vline & $7.42\%$ & \vline &$11.4\%$ & \vline & $0.552\%$ & \vline &$0.968\%$ & \vline & $0.141$ & \vline &$0.216$\\

\hline
\hline

\end{tabular}}
\label{ciTableIntrinsic}
\end{table*}

\begin{table*}[t!]
\centering
\caption{Mean 65\% and 90\% credible intervals of extrinsic parameters for
  each of the four systems considered.  As expected, there exists a
  substantial improvement in the sky localization capabilities of the
  four-detector HLVI configuration over the three-detector HLV
  configuration.  Note that the solid-angle sky-location confidence
  intervals, $\Delta\Omega$, are calculated directly on the 2D sphere,
  not by combining the $\alpha$ and $\delta$ uncertainties.}

  \tabcolsep=0.11cm
      {\renewcommand{\arraystretch}{1.3} 
\begin{tabular}{lcccccccccccccccccccc}
